Probabilistic Catalogs for Crowded Stellar Fields

### 2012-10-19 paper/ms.tex
Refer to powerlaw figure
Inference2

\section{Simulated Data}\label{sec:simulated_data}
We now apply the method to two illustrative simulated images generated from
the above model. The true parameter values used are listed in
Table~\ref{tab:truth}.
Each of the images
is $100 \times 100$ pixels in extent and covers a range from $-1$ to $1$ in
arbitrary units for both the $x$ and $y$ axes. The first image contains
$\sim$100 stars and the second image contains $\sim$1000 stars. The images
are shown in Figure~\ref{fig:simulated_data}.

@@

\subsection{Test Case 2}
{\bf Show inference on parameters}\\
{\bf Show phase transition}\\
{\bf Comment on computational speed}\\
{\bf Show a few catalogs}\\
{\bf Show posterior expected true scene}\\

>>>>

\section{Simulated Data}\label{sec:simulated_data}
We now apply the method to two illustrative simulated images generated from
the above model. The true parameter values used are listed in
Table~\ref{tab:truth}. The broken power-law parameter values were chosen so that
roughly half of the stars' fluxes were below and above the break-point
respectively. Figure~\ref{fig:powerlaw} also shows the true flux distribution
used for the simulated images. Each of the images
is $100 \times 100$ pixels in extent and covers a range from $-1$ to $1$ in
arbitrary units for both the $x$ and $y$ axes. The first image contains
$\sim$100 stars and the second image contains $\sim$1000 stars. The images
are shown in Figure~\ref{fig:simulated_data}.

@@

\subsection{Test Case 2}

\begin{figure}
\begin{center}
\includegraphics[scale=0.33]{Figures/inference2.eps}
\end{center}
\caption{Inference about the parameters for test case 2.\label{fig:results2}}
\end{figure}
